Model

### 2020-01-22 stats/model.Rmd
add model with RE

global_params_summary <- global_params %>%
  group_by(token, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

@@

plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~token, scales = 'free')+
  theme_few()

plot_global_params
```

@@

model_pred_prag_free<- bind_rows(
  readRDS("../saves/model_pred_pragmatic_free_chain1.rds")%>%mutate(chain = 1),
  readRDS("../saves/model_pred_pragmatic_free_chain2.rds")%>%mutate(chain = 2),
  readRDS("../saves/model_pred_pragmatic_free_chain3.rds")%>%mutate(chain = 3),
  readRDS("../saves/model_pred_pragmatic_free_chain4.rds")%>%mutate(chain = 4),
  readRDS("../saves/model_pred_pragmatic_free_chain5.rds")%>%mutate(chain = 5)
)

plot_model_pred_prag_free <- model_pred%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  group_by(model, alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

saveRDS(plot_model_pred_prag_free, "../saves/plot_model_pred_prag_free.rds")
plot_model_pred_prag_free <- readRDS("../saves/plot_model_pred_prag_free.rds")

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred_prag_free, aes(x=age+2,y = mean, col = model), size = 1)+
  geom_ribbon(data = plot_model_pred_prag_free, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

plot_model_prag_noise_line <- model_pred_prag_free%>%
  filter(iteration %in% x)

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(data = plot_model_prag_noise_line, aes(x=age+2,y = pred, col = factor(chain), group = interaction(chain,iteration)),size = .2, alpha = .05)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)
```

@@

cor_prag_free <- model_pred_prag_free%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  mutate(age = as.numeric(age) + min(me_data$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

saveRDS(cor_prag_free, "../saves/cor_prag_free.rds")
cor_prag_free <- readRDS( "../saves/cor_prag_free.rds")

cor_prag_noise <- model_pred_prag_noise%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  mutate(age = as.numeric(age) + min(me_data$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

saveRDS(cor_prag_noise, "../saves/cor_prag_noise.rds")
cor_prag_noise <- readRDS( "../saves/cor_prag_noise.rds")

cor_global_free <- model_pred_global_free%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  mutate(age = as.numeric(age) + min(me_data$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

cor_global_noise <- model_global_noise%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  mutate(age = as.numeric(age) + min(me_data$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

cor_model_pred <- bind_rows(
  cor_prag_free,
  cor_prag_noise
 # cor_global_free,
#  cor_global_noise
)

plot_cor_model_pred <- cor_model_pred %>%
  left_join(
    bind_rows(
      #binnned_data%>%mutate(model = "globalPrag_free"),
      #binnned_data%>%mutate(model = "globalPrag_noise"),
      binnned_data%>%mutate(model = "pragmatic_free"),
      binnned_data%>%mutate(model = "pragmatic_noise")
      )
  )

saveRDS(plot_cor_model_pred, "../saves/model_cor.rds")
plot_cor_model_pred <- readRDS( "../saves/model_cor.rds")

ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 1.5, stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(model~age)+
  theme_few() + 
  scale_colour_viridis_d(name ="Item")
```

>>>>

global_params_summary <- global_params %>%
  group_by (parameter,type)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

@@

plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(type~parameter, scales = 'free')+
  theme_few()

plot_global_params

plot_global_params %>%
  group_by(parameter, type)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))
```

@@

plot_model_pred <- model_pred%>%
  group_by(model, alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol()+
  scale_fill_ptol()

length(unique(model_pred$iteration))

x <- sample(1:10000, 500)

plot_model_prag__line <- model_pred%>%
  filter(model == "pragmatic", iteration %in% x)

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(data = plot_model_prag__line, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .05)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 2)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)
```

@@

cor_prag <- model_pred%>%
  filter(model == "pragmatic")%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

cor_global <- model_pred%>%
  filter(model == "global")%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

cor_flat <- model_pred%>%
  filter(model == "flat")%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

cor_prior <- model_pred%>%
  filter(model == "prior")%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

cor_model_pred <- bind_rows(
  cor_prag,
  cor_global,
  cor_flat,
  cor_prior
)

plot_cor_model_pred <- cor_model_pred %>%
  left_join(
    bind_rows(
      binnned_data%>%mutate(model = "pragmatic"),
      binnned_data%>%mutate(model = "global"),
      binnned_data%>%mutate(model = "flat"),
      binnned_data%>%mutate(model = "prior")
      )
  )

# saveRDS(plot_cor_model_pred, "../saves/model_cor.rds")
# plot_cor_model_pred <- readRDS( "../saves/model_cor.rds")

ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(model~age)+
  theme_few() + 
  scale_colour_ptol(name ="Alignment")
```
